%%%% GENERATED FILE - MODIFICATIONS MAY BE LOST %%%%
% LaTeX source of my resume
% =========================

% Commented for easy reuse... ;)

% See the `README.md` file for more info.

% This file is licensed under the CC-NC-ND Creative Commons license.


% start a document with the here given default font size and paper size
\documentclass[10pt,a4paper]{article}

% include the `tex` instructions that takes care of loading packages and defining commands

% Copyright (c) 2012 Cies Breijs
%
% The MIT License
%
% Permission is hereby granted, free of charge, to any person obtaining a copy
% of this software and associated documentation files (the "Software"), to deal
% in the Software without restriction, including without limitation the rights
% to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
% copies of the Software, and to permit persons to whom the Software is
% furnished to do so, subject to the following conditions:
%
% The above copyright notice and this permission notice shall be included in
% all copies or substantial portions of the Software.
%
% THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
% IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
% FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
% AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
% LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
% OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN THE
% SOFTWARE.


% Some commands for making a LaTeX resume
% =======================================

% Commented ;)

% See the README.md file for more info



% \documentclass[10pt,a4paper]{article}  % i do this in the document itself


%%% LOAD AND SETUP PACKAGES

\usepackage[a4paper,margin=0.75in]{geometry}
\usepackage{mdwlist}   % to finetue lists with a inline heading and indented content (see Experiences)
\usepackage{multicol}  % for multiple column text
\usepackage{relsize}   % for \textscale, which I prefer over \sc (small caps), see my \acr command
\usepackage[english]{babel}
\hyphenation{Some-long-word}

\usepackage{hyperref}  % yups, URLs everwhere...
\usepackage{xcolor}  % ... and color them links
\definecolor{dark-blue}{rgb}{0.15,0.15,0.4}
\hypersetup{colorlinks,linkcolor={dark-blue},citecolor={dark-blue},urlcolor={dark-blue}}

\usepackage{ifxetex}
\ifxetex
  \usepackage{fontspec}
%  \setmainfont
%    [ ExternalLocation ,
%      Mapping          = tex-text ,
%      Numbers          = OldStyle ,
%      Ligatures        = {Common,Contextual} ,
%      BoldFont         = texgyrepagella-bold.otf ,
%      ItalicFont       = texgyrepagella-italic.otf ,
%      BoldItalicFont   = texgyrepagella-bolditalic.otf ]
%    {texgyrepagella-regular.otf}
  % Comment out the previous statement and uncomment the following line to use the
  % Linux Libertine font (it has nice lignatures).
  % Make sure to have the `ttf-linux-libertine` package installed on Ubuntu.
\setmainfont[Mapping=tex-text, Numbers=OldStyle, Ligatures={Common,Contextual}]{Linux Libertine O}
  \usepackage[protrusion]{microtype}  % needs an experimental and impposible to find package for xetex
\else
  \usepackage{tgpagella}  % this case we lack lower case numbers, ligatures and some typographic niceties
  \usepackage[expansion,protrusion]{microtype}
\fi



%%% DOCUMENT WIDE STYLING

\pagestyle{empty}
\setlength{\tabcolsep}{0em}
\xspaceskip7pt  % some more spacing between sentences (use "i.e.\ " or "with SQL\@. " in case of errors)


%%% CUSTOM COMMANDS

% main title (name) with subtitle (date)
\newcommand*\maintitle[2]{\noindent{\LARGE \textbf{#1}}\ \ \ \emph{#2}}

% title for the root sections (experience, education, etc) of the resume
\newcommand*\roottitle[1]{\subsection*{#1}\vspace{-0.3em}\nopagebreak[4]}

% acr command, to quickly mark acronyms for special formatting
\newcommand*\acr[1]{\textscale{.85}{#1}}

% pretty bullet (created from a much smaller centerdot), \sbull contains its spacing
\newcommand*\bull{\raisebox{-0.365em}[-1em][-1em]{\textscale{4}{$\cdot$}}}
\newcommand*\sbull{\ \ \bull \ \ }

% it seems not to work when simply using \parindent...
\newlength{\newparindent}
\addtolength{\newparindent}{\parindent}

% a double \parindent...
\newlength{\doubleparindent}
\addtolength{\doubleparindent}{\parindent}
\addtolength{\doubleparindent}{\parindent}

% indentsection style, used for sections that aren't already in lists
% that need indentation to the level of all text in the document
\newenvironment{indentsection}%
{\begin{list}{}%
  {\setlength{\leftmargin}{\newparindent}\setlength{\parsep}{0pt}\setlength{\parskip}{0pt}\setlength{\itemsep}{0pt}\setlength{\topsep}{0pt}}%
}
{\end{list}}

% headerrow command, used for a new employer
\newcommand{\headedsection}[3]{\nopagebreak[4]\begin{indentsection}\item[]\textscale{1.1}{#1}\hfill#2#3\end{indentsection}\nopagebreak[4]}

% subheaderrow command, used for a new position
\newcommand{\headedsubsection}[3]{\nopagebreak[4]\begin{indentsection}\item[]\textbf{#1}\hfill\emph{#2}#3\end{indentsection}\nopagebreak[4]}

% body text (indented)
\newcommand{\bodytext}[1]{\nopagebreak[4]\begin{indentsection}\item[]#1\end{indentsection}\pagebreak[2]}



% \vspace variaties
\newcommand{\breakvspace}[1]{\pagebreak[2]\vspace{#1}\pagebreak[2]}
\newcommand{\nobreakvspace}[1]{\nopagebreak[4]\vspace{#1}\nopagebreak[4]}

% \spacedhrule a horizontal line with some vertical space before and after it
\newcommand{\spacedhrule}[2]{\breakvspace{#1}\hrule\nobreakvspace{#2}}

% \inlineheadsection command, used for a new employer
\newcommand{\inlineheadsection}[2]{\begin{basedescript}{\setlength{\leftmargin}{\doubleparindent}}\item[\hspace{\newparindent}\textbf{#1}]#2\end{basedescript}\vspace{-1.7em}}

% apo command, for an apostrophe that looks good on old style nums
\newcommand{\apo}{\raisebox{-.18ex}{'}{\hspace{-.1em}}}

% non space that allows line breaks
\newcommand*{\nsp}{\hskip0pt}

%%% MORE SPECIFIC COMMANDS

% CPP command (found it in some corner of the internet and decided to use it)
\newcommand{\CPP}{C\nolinebreak[4]\hspace{-.04em}\raisebox{.20ex}{\footnotesize\bf++} }

% KTurtle command :)
\newcommand{\KTurtle}{\acr{KT}urtle }



% % these are in the document itself:
%
% \begin{document}
% ...the document text...
% \end{document}



\begin{document}  % begin the content of the document
\sloppy  % this to relax whitespacing in favour of straight margins

\maintitle{Arjun Naik}{October 29, 1987}  % title on top of the document

\nobreakvspace{0.3em}  % add some page break averse vertical spacing

% \noindent prevents paragraph's first lines from indenting
% \mbox is used to obfuscate the email address
% \sbull is a spaced bullet
% \href well..
% \\ breaks the line into a new paragraph
\noindent\href{mailto:Arjun.RN@gmail.com}{Arjun.RN\mbox{}@\mbox{}gmail.com}\sbull
\textsmaller{+}49.17657886406
\sbull arjun-naik \emph{(Skype)}
\\
\sbull
\href{https://de.linkedin.com/in/arnaik}{https://de.linkedin.com/in/arnaik}
\sbull
\href{https://github.com/arjunrn}{https://github.com/arjunrn}
\\
Gret-Palucca-Stra{\ss}e 9, Whng. 1214\sbull
01069\sbull
Dresden\sbull
Germany

\spacedhrule{0.9em}{-0.4em}  % a horizontal line with some vertical spacing before and after

\roottitle{Summary}  % a root section title

\vspace{-1.3em}  % some vertical spacing
\begin{multicols}{2}  % open a multicolumn environment
\noindent \emph{An organised, meticulous, and resourceful software engineering with a focus on building distributed systems.}
\\
After obtaining a Bachelor's degree in Computer Science and Engineering I spent a year working at a consultancy. Here I got my first experience of participating in large projects and the responsibilities that come along with it. After that I moved to a startup where I built web applications and started developing Android apps. After working for 2 years in the industry I decided to continue my education in Germany. Studying at TU Dresden in the Systems Engineering chair has given me a unique opportunity to participate is several diverse research projects.

My goal is to work in an environment which fosters creativity and offers interesting challenges. Since I am a big proponent of open-source, I also wish that my work both utilises and contributes back to the community.

\end{multicols}

\spacedhrule{0em}{-0.4em}

\roottitle{Experience}

\headedsection
{\href{http://tu-dresden.de/die_tu_dresden/fakultaeten/fakultaet_informatik/sysa/se?set_language=en&cl=en}{TU Dresden}}
{\textsc{Dresden, Germany}}
{
 \headedsubsection
 {\acr{Wissenschaftliche Hilfskraft}}
 {Mar 2014 - Dec 2014}
 {\bodytext{
As a part of the {\href{http://tu-dresden.de/die_tu_dresden/fakultaeten/fakultaet_informatik/sysa/se/srex}{SREX(Secure Remote Execution)}} project developed a translator for C programs. A source C program is translated into a subset of C which can be encoded with redundant operations to ensure correct execution even in the event of bit-flips or other random transient errors.

More recently I have been working with distributed coordination services like ZooKeeper and Consul. I have been evaluating the efficacy and characteristics of the respective protocols(ZAB and Raft). Also implementing new features in Kazoo, a Python client library for Zookeeper.
	}
	\textbf{Technologies Used:} Python, Fabric, Apache ZooKeeper, C/C++, Scons, Consul, Mercurial
	}
}

\headedsection
{\href{http://dmfs.org/}{DMFS}}
{\textsc{Dresden, Germany}}
{
 \headedsubsection
 {\acr{Application Developer}}
 {Jan 2013 - March 2014}
 {\bodytext{
    DMFS develops data sync applications for the Android platform. I worked on the development of the {\href{https://play.google.com/store/apps/details?id=org.dmfs.tasks}{Tasks}} app which uses the CalDav protocol to sync calendar data. This app was subsequently open-sourced and available on {\href{https://github.com/dmfs/tasks}{Github}}.Was also part of the team which developed an Android based {\href{https://play.google.com/store/apps/details?id=com.schedjoules.calstore}{Calendar Store}}.
    
    But my primary role was as a Django developer. Developed a web service for the bulk-retail of mobile apps. The service used OpenSSL cryptography to sign and verify the source of the sold apps. Only apps with a valid key issued from the website could be activated. Also developed the Android SDK which integrates with existing third-party apps to provide this functionality.
	}
	\textbf{Technologies Used:} Python, Android, Django, OpenSSL, PostgreSQL, Git
	}

}

\headedsection
{\href{http://www.notiphi.com}{Locus Labs}}
{\textsc{Bangalore, India}}
{
 \headedsubsection
 {\acr{Web and Mobile Developer}}
 {Jun 2011 - August 2012}
 {\bodytext{
 When I joined Locus Labs it was an unseeded startup which developed apps for the up-scale and savvy shopper. The main product {\href{http://www.notikum.com}{Notikum}} finds offers and bargains for shoppers based on their profile. This involved collecting data from hundreds of websites. Joined the team which scraped the data and indexed it with Solr. Concurrently developed and maintained the website for this service. The surge in mobile apps necessitated that an Android app be developed which I initially managed and later coordinated with new hires.

After the startup pivoted was given further responsibilities. I was put in charge of the development of the new product {\href{http://www.notiphi.com}{Notiphi}}. Location based advertising was the primary goal of this service. Designed and implemented the initial prototype. Also developed the tools needed for the deployment and monitoring of the cloud-based infrastructure. Leveraged my previous Android experience to develop the Android SDK which is used by third-party developers to integrate this service into their apps.}
	\textbf{Technologies Used:} Django, Python, Android, Tornado, Fabric, Scrapy, Javascript, JQuery, MySQL, MongoDB, Redis, Git
	}	
}

\headedsection  % sets the header for the section and includes any subsections
{\href{http://www.netbramha.com}{Netbramha Studios}}
{\textsc{Bangalore, India}}
{
  \headedsubsection  % sets the header for a subsection and contains usually body text
    {\acr{Web Developer}}
    {Oct 2010 - May 2011}
    {\bodytext{Netbramha Studios is a design consultancy which develops aesthetic and content intensive websites. I was hired to handle the technical aspects: Maintenance of websites and minor front-end development. I also built websites using both third-party and in-house server frameworks. Used JQuery for front-end development and also did some basic layout and styling with \acr{HTML+CSS}.
    
    }
    \textbf{Technologies Used:} PHP, CodeIgniter, CakePHP, JQuery, Javascript, Python, Django, SVN, Git}
}

\begin{center}
  \emph{Please consult my \href{https://de.linkedin.com/in/arnaik}{LinkedIn Profile} for references.}
\end{center}


\spacedhrule{-0.2em}{-0.4em}

\roottitle{Education}

\headedsection
  {Techniche Universit{\"a}t Dresden}
  {\textsc{Dresden, Germany}} {%
  \headedsubsection
    {Master of Science, Distributed Systems Engineering}
    {2012 -- 2014}
    {\bodytext{
        Completed courses in Security and Cryptography, Software Fault Tolerance and Dependable Systems besides the mandatory courses. Also worked in the Systems Engineering Lab and Software Fault Tolerance Lab. Under the guidance of Prof. Dr. Christof Fetzer completed my Master's Thesis in Zookeeper scaling. The proposed solution partitions the namespace which increases the throughput and avoids the negative effects of horizontal scaling.}
    }
}

\headedsection
  {BM Sreenivasaiah College of Engineering, Vivesvararya Technological University}
  {\textsc{Bangalore, India}} {%
  \headedsubsection
    {Bachelor of Computer Science and Engineering}
    {2006 -- 2010}
    {\bodytext{
        Major in Computer Science with a focus on Computer Architecture. Was also an editor of the departmental newsletter and a regular contributor. For my final year project developed a Wi-Fi enabled robot which could be controlled over the Internet. It also had a plethora of sensors which guided in navigation and control.}
    }
}

\spacedhrule{1.6em}{-0.4em}

\roottitle{Projects}

\headedsection{
{\href{http://se.inf.tu-dresden.de/pubs/papers/Wamhoff2014a.pdf}{JoQuer: Turbo frequency scaling libraries}}
}
{\bodytext{Current generation processors like the Intel Haswell series have the ability to temporarily boost the clock frequency through software. A C++ library was developed at the Systems Engineering chair at TU Dresden to provide this functionality to applications and manage the application threads. I constructed a Java library with a similar API. The library used JNI(Java Native Interface) to interact with the C++ library. After the library was implemented, benchmarked and recorded the results to compare the effect of boosting frequency in Java applications.}
}

\headedsection{Studybloxx: Android list sync application
{\href{https://github.com/arjunrn/studybloxx-server}{(https://github.com/arjunrn/studybloxx-server)}}
}
{\bodytext{For a course in Mobile Application Development my team developed an application for Android which syncs relational data across devices. The sync is performed through a Django web server using a \acr{REST API}. To further improve the application functionality LibGit2 was cross-compiled to run on Android and sync data. Git is used to handle the issues arising out of concurrent modification of data from multiple sources.}
}

\spacedhrule{0.5em}{-0.4em}

\roottitle{Skills}

\inlineheadsection  % special section that has an inline header with a 'hanging' paragraph
  {Technical Specialities:}
  {Good skills in Python, Java, Javascript. Can also program in C/C++. Most experience with Python. Interested in using Go language in a professional setting. Also a solid grasp of Front-End web technologies: \acr{HTML+CSS}, JavaScript(jQuery, Angular.js). Version Control Systems: Git, Mercurial and SVN. Experience with developing Android applications. Also used and configured databases like MySQL, PostgreSQL, MongoDB and Redis. For the past 6 years have been using Linux both on servers and on desktops.

}

\inlineheadsection
  {Natural Languages:}
  {English \emph{(Bilingual Proficiency)}, Hindi \emph{(Native)}, Kannada \emph{(Native)},German \emph{(Limited proficiency)}.}


\spacedhrule{1.6em}{-0.4em}

\roottitle{Interests}

\inlineheadsection
  {Non-exhaustive and in no particular order:}
  {Science-Fiction, photography, hardware hacking, travelling, good coffee}


\end{document}
