%%%% GENERATED FILE - MODIFICATIONS MAY BE LOST %%%%
% LaTeX source of my resume
% =========================

% Commented for easy reuse... ;)

% See the `README.md` file for more info.

% This file is licensed under the CC-NC-ND Creative Commons license.


% start a document with the here given default font size and paper size
\documentclass[10pt,a4paper]{article}

% include the `tex` instructions that takes care of loading packages and defining commands

% Copyright (c) 2012 Cies Breijs
%
% The MIT License
%
% Permission is hereby granted, free of charge, to any person obtaining a copy
% of this software and associated documentation files (the "Software"), to deal
% in the Software without restriction, including without limitation the rights
% to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
% copies of the Software, and to permit persons to whom the Software is
% furnished to do so, subject to the following conditions:
%
% The above copyright notice and this permission notice shall be included in
% all copies or substantial portions of the Software.
%
% THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
% IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
% FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
% AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
% LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
% OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN THE
% SOFTWARE.


% Some commands for making a LaTeX resume
% =======================================

% Commented ;)

% See the README.md file for more info



% \documentclass[10pt,a4paper]{article}  % i do this in the document itself


%%% LOAD AND SETUP PACKAGES

\usepackage[a4paper,margin=0.75in]{geometry}
\usepackage{mdwlist}   % to finetue lists with a inline heading and indented content (see Experiences)
\usepackage{multicol}  % for multiple column text
\usepackage{relsize}   % for \textscale, which I prefer over \sc (small caps), see my \acr command
\usepackage[english]{babel}
\hyphenation{Some-long-word}

\usepackage{hyperref}  % yups, URLs everwhere...
\usepackage{xcolor}  % ... and color them links
\definecolor{dark-blue}{rgb}{0.15,0.15,0.4}
\hypersetup{colorlinks,linkcolor={dark-blue},citecolor={dark-blue},urlcolor={dark-blue}}

\usepackage{ifxetex}
\ifxetex
  \usepackage{fontspec}
%  \setmainfont
%    [ ExternalLocation ,
%      Mapping          = tex-text ,
%      Numbers          = OldStyle ,
%      Ligatures        = {Common,Contextual} ,
%      BoldFont         = texgyrepagella-bold.otf ,
%      ItalicFont       = texgyrepagella-italic.otf ,
%      BoldItalicFont   = texgyrepagella-bolditalic.otf ]
%    {texgyrepagella-regular.otf}
  % Comment out the previous statement and uncomment the following line to use the
  % Linux Libertine font (it has nice lignatures).
  % Make sure to have the `ttf-linux-libertine` package installed on Ubuntu.
\setmainfont[Mapping=tex-text, Numbers=OldStyle, Ligatures={Common,Contextual}]{Linux Libertine O}
  \usepackage[protrusion]{microtype}  % needs an experimental and impposible to find package for xetex
\else
  \usepackage{tgpagella}  % this case we lack lower case numbers, ligatures and some typographic niceties
  \usepackage[expansion,protrusion]{microtype}
\fi



%%% DOCUMENT WIDE STYLING

\pagestyle{empty}
\setlength{\tabcolsep}{0em}
\xspaceskip7pt  % some more spacing between sentences (use "i.e.\ " or "with SQL\@. " in case of errors)


%%% CUSTOM COMMANDS

% main title (name) with subtitle (date)
\newcommand*\maintitle[2]{\noindent{\LARGE \textbf{#1}}\ \ \ \emph{#2}}

% title for the root sections (experience, education, etc) of the resume
\newcommand*\roottitle[1]{\subsection*{#1}\vspace{-0.3em}\nopagebreak[4]}

% acr command, to quickly mark acronyms for special formatting
\newcommand*\acr[1]{\textscale{.85}{#1}}

% pretty bullet (created from a much smaller centerdot), \sbull contains its spacing
\newcommand*\bull{\raisebox{-0.365em}[-1em][-1em]{\textscale{4}{$\cdot$}}}
\newcommand*\sbull{\ \ \bull \ \ }

% it seems not to work when simply using \parindent...
\newlength{\newparindent}
\addtolength{\newparindent}{\parindent}

% a double \parindent...
\newlength{\doubleparindent}
\addtolength{\doubleparindent}{\parindent}
\addtolength{\doubleparindent}{\parindent}

% indentsection style, used for sections that aren't already in lists
% that need indentation to the level of all text in the document
\newenvironment{indentsection}%
{\begin{list}{}%
  {\setlength{\leftmargin}{\newparindent}\setlength{\parsep}{0pt}\setlength{\parskip}{0pt}\setlength{\itemsep}{0pt}\setlength{\topsep}{0pt}}%
}
{\end{list}}

% headerrow command, used for a new employer
\newcommand{\headedsection}[3]{\nopagebreak[4]\begin{indentsection}\item[]\textscale{1.1}{#1}\hfill#2#3\end{indentsection}\nopagebreak[4]}

% subheaderrow command, used for a new position
\newcommand{\headedsubsection}[3]{\nopagebreak[4]\begin{indentsection}\item[]\textbf{#1}\hfill\emph{#2}#3\end{indentsection}\nopagebreak[4]}

% body text (indented)
\newcommand{\bodytext}[1]{\nopagebreak[4]\begin{indentsection}\item[]#1\end{indentsection}\pagebreak[2]}



% \vspace variaties
\newcommand{\breakvspace}[1]{\pagebreak[2]\vspace{#1}\pagebreak[2]}
\newcommand{\nobreakvspace}[1]{\nopagebreak[4]\vspace{#1}\nopagebreak[4]}

% \spacedhrule a horizontal line with some vertical space before and after it
\newcommand{\spacedhrule}[2]{\breakvspace{#1}\hrule\nobreakvspace{#2}}

% \inlineheadsection command, used for a new employer
\newcommand{\inlineheadsection}[2]{\begin{basedescript}{\setlength{\leftmargin}{\doubleparindent}}\item[\hspace{\newparindent}\textbf{#1}]#2\end{basedescript}\vspace{-1.7em}}

% apo command, for an apostrophe that looks good on old style nums
\newcommand{\apo}{\raisebox{-.18ex}{'}{\hspace{-.1em}}}

% non space that allows line breaks
\newcommand*{\nsp}{\hskip0pt}

%%% MORE SPECIFIC COMMANDS

% CPP command (found it in some corner of the internet and decided to use it)
\newcommand{\CPP}{C\nolinebreak[4]\hspace{-.04em}\raisebox{.20ex}{\footnotesize\bf++} }

% KTurtle command :)
\newcommand{\KTurtle}{\acr{KT}urtle }



% % these are in the document itself:
%
% \begin{document}
% ...the document text...
% \end{document}

\begin{document}  % begin the content of the document
\sloppy  % this to relax whitespacing in favour of straight margins

\maintitle{Rodrigo Lins de Oliveira}{March 7, 1981}  % title on top of the document

\nobreakvspace{0.3em}  % add some page break averse vertical spacing

% \noindent prevents paragraph's first lines from indenting
% \mbox is used to obfuscate the email address
% \sbull is a spaced bullet
% \href well..
% \\ breaks the line into a new paragraph
\noindent\href{mailto:lins.oliveira.at.gmail.com}{lins.oliveira\mbox{}@\mbox{}gmail.com}
\sbull\textsmaller{+}49.1520.2648443\sbull rodrigo\_nanoinfo \emph{(Skype)} \\
\href{https://www.linkedin.com/in/rodrigolins}{www.linkedin.com/in/rodrigolins}\sbull\href{https://github.com/rodrigolins}{github.com/rodrigolins} \\
Hansastra{\ss}e\sbull
01097\sbull
Dresden\sbull
Germany

\spacedhrule{0.9em}{-0.4em}  % a horizontal line with some vertical spacing before and after

\roottitle{Summary}  % a root section title

\vspace{-1.3em}  % some vertical spacing
\begin{multicols}{2}  % open a multicolumn environment
%\noindent \emph{Creative geek with roots in the open source movement, an entrepreneurial mindset and a passion for user/customer centered software development with maintainable outcomes.}
\noindent \emph{Fastidious, meticulous, eloquent software engineer with focus on software architecture and systems engineering.}
\\
\\
Started to work in a IT consultancy company in 2003 as a network administrator. Working with computer networks in Windows and Linux environments I thought that I could start my own business. In 2004, I started a small business to help companies with their IT infrastructure, not only the network infrastructure but all IT aspect. At some point I was working for nine different companies.

In 2007 I joined the \acr{CEFET/RJ} university where I graduate in 2011 in Internet Systems with honors.

During my college studies I closed my business and joined Target Solutions professional services to work full time. At this point, I was working with open source technologies on a daily basis, and I love it! At Target Solutions, I worked as an outsourced employee at Alcatel-Lucent Technoligies and at Oi (the biggest ISP in Brazil). In those companies I worked in different sizes of teams, with different responsibilities in several projects. I worked in large scale projects like network troubleshooting tools, fraud detection and to users information management to be used by the government judiciary.

In 2011 I decided to move in to Germany to study at \acr{TU} Dresden where I obtained my master degree in Distributed Systems Engineering. While living in Dresden I worked for two companies as a software architect and operations. At Exelonix we developed a custom Android and smart home devices for elderly people. I worked developing the platform infrastructure and managing the company's internal tools.

%Upon my graduation I'm keen to work in a creative and innovative environment. Since I'm an open source enthusiast I would like to work with open source software and to give it back to the community.

Upon my graduation I'm keen to work in a company which values creativity and innovation. That also provides a fertile soil for using open sources technologies and contributes to the community.

\end{multicols}

\spacedhrule{0em}{-0.4em}

\roottitle{Experience}

\headedsection  % sets the header for the section and includes any subsections
  {\href{http://www.exelonix.com}{Exelonix GmbH}}
  {\textsc{Dresden, Germany}} {%
  \headedsubsection  % sets the header for a subsection and contains usually body text
    {Software Engineer \& \acr{DevOps}}
    {Aug \apo14 -- present}
    {\bodytext{Exelonix is a company focused to improve quality of life for the elderly. The main product is the \href{https://www.asina-tablet.de/}{Asina Tablet}, that is a custom android version for elderly people. They also produces smart house appliances and health monitoring appliances. In the company I worked as a full stack developer producing the \href{https://www.asina-tablet.de/}{Asina Tablet} website using python and \href{https://wagtail.io/}{wagtail}. I also created a simple e-commerce plugin for wagtail to sell their products on-line. Developed a newsletter tool in Django to manage and track their newsletter. My roles also included research, installation, configuration and management of several supporting tools like Icinga, Nagios, Jenkins. Enforcing the platform security using \acr{IPSec} \acr{VPN} \href{https://www.strongswan.org/}{strongSwan} and create own public key infrastructure (\acr{PKI}). Joined Cebit and IFA congresses for the product promotion.
		}
	\textbf{Technologies Used:} Java, Java Portlets, Python, Fabric, PostgreSQL, Django, Wagtail, Redis, Nginx, Apache, Linux, IPSec, OpenSSH, Mercurial.	
	}
}

\headedsection
  {\href{http://www.inquence.com/}{Inquence GmbH}}
  {\textsc{Dresden, Germany}} {%
  \headedsubsection
    {\acr{Software Developer}}
    {Apr \apo13 -- Jul \apo14}
    {\bodytext{Inquence GmbH is a company focused on content management systems that provides dynamic search and integration with third-party applications. The product included a web platform and a client machine to be added at the costumer network. All documents form the user should be available anywhere at anytime. At Inquence my responsibilities includes requirement gathering, implementation and testing of new features and management of legacy code. I was also in charge of orchestration and maintenance of the clients and the platform updates.}
    \textbf{Technologies Used:} Java, Python, Fabric, Ansible, MySQL, Linux, Git, PHP.
    }
}

\headedsection
  {\href{http://www.targetso.com}{Target Solutions}}
  {\textsc{Rio de Janeiro (\acr{RJ}), Brazil}} {%
  \headedsubsection
    {Software Developer}
    {Jan \apo09 -- Dec \apo11}
    {\bodytext{Target solutions is a professional service consultancy company that provides outsourced specialists and software development. When I joined Target Solutions I was allocated at Alcatel-Lucent Technologies to help their development team. In Alcatel-Lucent I worked developing a user troubleshooting and fraud detection tool for the main ISP company in Brazil. Later, I was reassigned to work in a project to troubleshoot the ISP backbone. After that, I join in another team to develop a tool to record the user connection information to be used by the brazilian judiciary to identify the user subscribers.}
    \textbf{Technologies Used:} Java, Maven, Spring, Hibernate, Struts, EJB, SNMP, Corba, JAX-WS, Selenium, JUnit, Aspect4J, MySQL Server, Subversion, Linux, Solaris.
    }
}

\headedsection
  {\href{http://www.nanoinfo.com}{Nanoinfo}}
  {\textsc{Rio de Janeiro (\acr{RJ}), Brazil}} {%
  \headedsubsection
    {\acr{IT} Consultant}
    {Nov \apo04 -- Jan \apo09}
    {\bodytext{Nanoinfo was my private company were I provide IT consultancy for other business. At Nanoinfo I worked for several costumers from different sectors providing all types of consultancy. The consultancy included installation of the network infrastructure, setup of windows server or linux server to manage the users, computers, printers with Active Directory or Samba, configuration and management of system shares, mail server (MS exchange), phone gateways (Asterix), firewalls (ISA Server or pfSense).
    }
	\textbf{Technologies Used:} Windows 2003 Server, Windows XP, Linux, Active Directory, Samba, NFS, DHCP, DNS, Microsoft Exchange Server, Microsoft ISA server, pfSense, Asterix.
    }
}

\begin{center}
  \emph{Please refer to my \href{www.linkedin.com/in/rodrigolins}{LinkedIn} profile for complete reference and recommendations.}
\end{center}

\spacedhrule{-0.2em}{-0.4em}

\roottitle{Education}

\headedsection
  {Techniche Universit{\"a}t Dresden}
  {\textsc{Dresden, Germany}} {%
  \headedsubsection
    {Master of Science, Distributed Systems Engineering}
    {2012 -- 2016}
    {\bodytext{Completed courses in Security and Cryptography, Software Fault Tolerance, Distributed Operating Systems and Real-Time Systems besides the mandatory courses. Also worked in the Software Fault Tolerance Lab. Under the guidance of Prof. Dr. rer. nat. habil. Uwe A{\ss}mann completed my master's thesis in error modeling in context-aware systems. The proposed solution qualifies the sensed data and creates a inference rule mechanism to detect errors.}
    }
  }

\headedsection
  {Centro Federal de Educação Tecnológica Celso Suckow da Fonseca - \acr{CEFET/RJ}}
  {\textsc{Rio de Janeiro (\acr{RJ}), Brazil}} {%
  \headedsubsection
    {Bachelor, Internet Systems}
    {2007 -- 2011}
    {\bodytext{Completed major in Internet Systems with emphasis online systems. Also managed the faculty computer network infrastructure. Under the guidance of Prof. Dr. Eduardo Bezerra completed my bachelor's thesis in finding correlation among stocks. The proposed work found a similar behavior among stocks using machine learning algorithms.}
    }
  }

\spacedhrule{0.5em}{-0.4em}

\roottitle{Awards}

\headedsection
  {Centro Federal de Educação Tecnológica Celso Suckow da Fonseca - \acr{CEFET/RJ}}
  {\textsc{Rio de Janeiro (\acr{RJ}), Brazil}} {%
  \headedsubsection
    {Academic Honor}
    {2011}
    {\bodytext{Rewarded with the highest student award for academic excellence from my university.}
    }
  }

\spacedhrule{1.6em}{-0.4em}

\roottitle{Publications}

\headedsection
  {\href{http://www.archplus.net/}{ARCH+ Magazine}}
  {\textsc{Berlin, Germany}} {%
  \headedsubsection
    {\href{http://www.archplus.net/home/archiv/artikel/46,4039,1,0.html}{Data Visualization of Climate Change - United Nation data visualised}}
    {2013}
    {\bodytext{ARCH+ is one of the oldest and largest magazines in Germany that focus on architectural history and theory. Every issue is devoted to a particular subject. In the issue about a critic of the contemporary (\textit{Kritik der Gegenwart}) we submit an article tracing a parallel between the carbon dioxide emissions and gross national income (\acr{GNI}) to show that there is a direct correlation between the \acr{GNI} and carbon dioxide emissions. We also trace a parallel between the carbon dioxide emission and the population affected due natural disasters to show that the poorest countries are more affected with the carbon dioxide emissions. In this publication I developed the algorithm to acquire the data from the UN database, the sorting algorithms and the plot algorithm using \href{https://processing.org/}{processing}.}
    }
  }

\spacedhrule{0.5em}{-0.4em}

\roottitle{Projects}
  
\headedsection{
{\href{https://github.com/Eden-06/TRoML}{Textual Role Modeling Language (\acr{TRoML})}}
}
{\bodytext{The Textual Role Modeling Language (\acr{TRoML}) is a simple textual modeling language to create instances of the \acr{CROM} metamodel. The Compartment Role Object Metamodel (CROM) is a comprehensive model for role-based modeling and programming languages. In this project I developed the domain specific language for \acr{CROM} in \acr{TRoML} using \href{https://eclipse.org/Xtext/}{Xtext}. It was develop during my internship at the \textit{Software Technology Group} in the \textit{TU Dresden}.}
}

\spacedhrule{0.5em}{-0.4em}

\roottitle{Skills}

\inlineheadsection  % special section that has an inline header with a 'hanging' paragraph
  {Technical specialties:}
  {Solid understanding in Java and related technologies (Spring, \acr{JPA}, \acr{EJB}, \acr{GWT}). Good understanding in Python, C/C++ and Ruby. Advance knowledge of web technologies:\ \acr{HTML5}, \acr{CSS3}, JavaScript(jQuery). Version control systems:\ Mercurial, Subversion and Git. Database systems:\ PostgreSQL, MySQL, Redis. Linux administration:\ \acr{zsh}, Apache, nginx, orchestration (Ansible and Chef), continuous integration (Jenkins), \acr{IPSec}, Nagios, Icinga, firewall (pfSense), samba, dhcp. Communication protocols: \acr{SNMP}. Windows Server administration:\ ISA Server, Active Directory, Exchange Server.
  }

\inlineheadsection
  {Natural languages:}
  {Portuguese \emph{(mother tongue)}, English \emph{(full professional proficiency)}, German \emph{(limited proficiency)}.}

\spacedhrule{1.6em}{-0.4em}

\roottitle{Interests}

\inlineheadsection
  {Non-exhaustive and in no specific order:}
  {Programming, Data Visualization, Cinema, Electronics, Open Source, Board Games, Card Games, Hardware Hacking, Brazilian Jiu-Jitsu, Travel and Cooking.}

\end{document}
